Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Summer Wrap Up

### 2023-08-08 aug08meeting_pres4/may30ccgmeeting.tex
updates

	\section{Next Steps/Future Work}
	\begin{frame}{Next Steps for Synthetic Lethality Analysis}
		\begin{enumerate}
			\item Refine the current list of synthetic lethal pairs by performing survival analysis to identify SL pairs that contribute to improved patient survival.
			\item Build male and female synthetic lethal interaction networks
		\end{enumerate}
	\end{frame}

	\begin{frame}{}
		content...
	\end{frame}

>>>>

	\section{Next Steps/Future Work}
	\begin{frame}{Next Steps for Synthetic Lethality Analysis}
		\begin{enumerate}
			\item Refine the current list of synthetic lethal pairs by performing survival analysis to identify SL pairs that contribute to improved patient survival.
			\item Build male and female synthetic lethal interaction networks	
		\end{enumerate}
	\includegraphics[width=12cm, height=6cm]{network_interactions.png}
	\end{frame}

	\section{Limitations}
	\begin{frame}{A Major Limitation}
		In many cancers, normal tissues are not available in The Cancer Genome Atlas	
		\begin{center}
			\includegraphics[width=6cm, height=6cm]{lack.png}
		\end{center}
	\footnotetext[1]{\tiny Figure From  \cite{zeng2019selecting}}
	\end{frame}

	\section{Takeaways \& Tips}
	\begin{frame}{Experience Gained (Technical Skills)}

	\begin{frame}{Experience Gained (Personal Skills)}
		content...
	\end{frame}

	\begin{frame}{Major Takeaways for Future Undergrads}
		\begin{itemize}
			\item 
		\end{itemize}
	\end{frame}

	\begin{frame}{Thank You}
		To Sushant for taking a chance on me

		To everyone in the lab for the constant support and guidance

		11/10 would do again

		\begin{center}
			\includegraphics[width=7cm, height=5cm]{lab.jpg}
		\end{center}
	\end{frame}
